Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-11-03 main.tex
Fixed tikz picture as per request

To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (3.375,3.375) rectangle (5.625,2.625);
    \node at (4.5,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
    \fill [lightgray] (0.875,3.375) rectangle (3.125,2.625);
    \node at (2,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

@@

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3.25) {\Large$\mathcal{A}'$};
    \node at (3.25,5.5) {\Large$\mathcal{A}$};
    \node at (3.25,0.5) {\Large$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO secure\\scheme};
    \draw [-latex] (2,1.75) -- (2,2.75);

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO secure\\scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{High-level overview of our scheme's LCAO security proof.}
\label{fig:proof_summary}
\end{figure}

>>>>

To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (2.125,3.375) rectangle (4.375,2.625);
    \node at (3.25,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

@@

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3) {\Large$\mathcal{A}'$};
    \node at (3.25,5.5) {\Large$\mathcal{A}$};
    \node at (3.25,0.5) {\Large$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
    \draw [-latex] (2,1.75) -- (2,2.5);

    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{High-level overview of our scheme's LCAO security proof.}
\label{fig:proof_summary}
\end{figure}

### 2020-11-03 tikz_images/proof.tex
Completed a lot more changes - many wording consistencies - many equation numbering consistencies - many notation consistencies - some figures updated a little bit as well - etc... - 2 additions remain
Fixed tikz picture as per request

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
    \draw [-latex] (2,1.75) -- (2,2.75);

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
\end{tikzpicture}

>>>>

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3) {\Large$\mathcal{A}'$};
    \node at (3.25,5.5) {\Large$\mathcal{A}$};
    \node at (3.25,0.5) {\Large$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
    \draw [-latex] (2,1.75) -- (2,2.5);

    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
\end{tikzpicture}
